### 2013-11-26 PositionPaper/useCase.tex
Use Case

\begin{figure*}
\includegraphics[width=0.8\textwidth]{figs/arch.png}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure*}

@@

In our approach energy producers are modelled as services with associated ``agreed'' SLAs. 
In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. In our example assume that there are several energy provision services (e$_1$, ... e$_n$) that can be independent or hubs:
\begin{description}
\item energyProvider.requestAvailability() $\rangle$ $<$ KWatt/h, cost, rate, location $>$ $\langle$

\item energyHub.requestAvailability() $\rangle$ $<$ {ID, KWatt/h, cost, rate, location $>$}$\langle$
\end{description}

@@

>>>>

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/arch.png}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure}

@@

In our approach energy producers are modelled as services with associated ``agreed'' SLAs. 
In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers:
\begin{description}
\sf\footnotesize
\item energyProvider.requestAvailability() $\rightarrow$ $\langle$KWatt/h, Ecost, rate, location$\rangle$

\item energyHub.requestAvailability() $\rightarrow$  \{$\langle$ID, KWatt/h, cost, rate, location$\rangle$\}

\end{description}

Each service is deployed in different cloud provider and each exports an agreed SLA that specifies {\sf agreedSLA:$\langle$cost/call, maxCalls, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}. Cloud providers define also their SLA contracts defining {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}.

@@

 \paragraph{Derived SLA}

  \paragraph{Computing service compositions}

   \paragraph{Optimizing service compositions execution}
